---
title: "Assignment B-1: Making a function"
output: github_document
---

1. Load the needed packages below.

```{r}
library(palmerpenguins)
library(dplyr)
library(tibble)
library(testthat)
```

2. Exercise 1: Make a Function and Exercise 2: Document your Function

Make a function that bundles a specific **group_by() %>% summarise()** workflow and document the function using **roxygen2 tags**

```{r}
#' Median Value in Each Group
#'
#' The function groups all data in a tibble by variable `group`  
#' and get the median of a numerical variable `x` in each group
#'
#' @param data - The input data that you are interested in to get the median value of each group in the tibble
#' @param var_x - A numerical variable x in the data that you are interested in to get the median value in each group
#' @param var_group - A variable in the data that you want to use it to group the data
#' @param na.rm - A parameter determines if remove NA values or not when getting the median
#' 
#' @return The function returns the median values of var_x in each var_group, which should be a tibble


median_in_group <- function(data, var_x, var_group, na.rm) {

  # determine if the input data is a tibble
  # determine if the variable x that you want to get median values is in numerical format 
  # use deparse(substitute(var_x)) to get the name of the var_x 
  # data[["name of a variable"]] can help extract the column
  if(!is_tibble(data) || !is.numeric(data[[deparse(substitute(var_x))]])) {
    stop('The data should be a tibble and the variable x should be in numerical format.')
  }
  
  median_values <- data %>% # load data
    group_by({{var_group}}) %>% # group data by `var_group`
    summarise(median = median({{var_x}}, na.rm = na.rm)) # get the median of var_x in each group, you can remove NA values or not
  
  return(median_values) 
}
```

3. Exercise 3: Include examples

Use penguins data set to show different examples.
```{r}
head(penguins)
```

Get the median values of body_mass_g in each island (remove NA values when getting the median values):

```{r}
median_in_group(penguins, body_mass_g, island, TRUE)
```

Get the median values of bill_length_mm in each species (not remove NA values when getting the median values):

```{r}
median_in_group(penguins, bill_length_mm, species, FALSE)
```


An example that deliberately show an error: input data should be a tibble and var_x should be a numerical variable

```{r, error = TRUE}
median_in_group(penguins, island, year)
```

4. Exercise 4: Test the Function

Test the function with multiple non-redundant inputs:

```{r}
# Get the correct median of body_mass_g (remove NA values) in each island to help for testing 
median_body_mass_g_in_island <- penguins %>%
  group_by(island) %>%
  summarise(median = median(body_mass_g, na.rm = TRUE))

# Get the correct median of body_mass_g (not remove NA values) in each island to help for testing
median_body_mass_g_NA_in_island <- penguins %>%
  group_by(island) %>%
  summarise(median = median(body_mass_g, na.rm = FALSE))

test_that("Test median_in_group function", {
  # expect the function to get the same result as median_body_mass_g_in_island
  expect_equal(median_in_group(penguins, body_mass_g, island, TRUE), median_body_mass_g_in_island)
  # expect the function to get the same result as median_body_mass_g_NA_in_island
  expect_equal(median_in_group(penguins, body_mass_g, island, FALSE), median_body_mass_g_NA_in_island)
  # expect the return of the function to be a tibble
  expect_equal(is_tibble(median_in_group(penguins, body_mass_g, island, TRUE)), TRUE)
  # expect the var_x to be a numerical variable instead of a categorical variable
  expect_error(median_in_group(penguins, island, year))
  # expect the input data to be a tibble instead of a list
  expect_error(median_in_group(c("Biscoe", "Dream", "Torgersen"), island, year))
  # expect the input data to be a tibble instead of a number
  expect_error(median_in_group(numeric(1), island, year))
}) 
```

